---
name: Charles
surname: Bonk
position: "Graduate Student  ||   Univeristy of Nebraska - Lincoln"
address: "5733 S 98th Plz 3B, Omaha, NE"
phone: +1 402 440 2651
email: "ctbonk0@protonmail.com"
twitter: CharlieBonk
github: charlestbonk
linkedin: charles-bonk
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Masters in Statistics", "2022-24", "University of Nebraska - Lincoln", "Lincoln, Nebraska",
  "Bachelor of Science - Mathematics", "2018-22", "University of Nebraska - Lincoln", "Lincoln, Nebraska"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Related Courses

* Statistics
  * Statistics and Applications
  * Introduction to Statistics II
  * Introduction to Mathematical Statistics I: Distribution Theory
  * Introduction to Mathematical Statistics II: Statistical Inference
* Mathematics
  * Multivariate Calculus
  * Linear Algebra
  * Theory of Linear Transformations
  * Math in the City (Applicative Mathematics)

# Technical Skills

* Coding in:
  * R
  * MATLAB
  * LaTeX
  * Python
  * SQL
  * SAS

[//]: <> (Ouch. Template gotta flex on me on not having a Nobel.)
# Relvant Experience

```{r}
tribble(
  ~Year, ~Type, ~Where, ~Desc,
  2021, "Statistics Intern", "Lincoln Police Department - Lincoln, NE","Mange and analyse large sets of confidential police case data.",
  2020, "Mathematics Department Teaching Assistant","University of Nebraska-Lincoln - Lincoln, NE", "Lead classes of over 20 students through reciation materials covering multivariate calculus."
) %>% 
  detailed_entries(
    Type,
    Year,
    Where,
    Desc
  )
```


# Projects

```{r}
tribble(
   ~Position, ~ProjectType, ~Desc, ~Year,
  "University of Nebraska - Lincoln | MATH 435: Math in the City", "Capstone Project", "COVID-19 Vaccine and Variant Interactiosn: An Analysis of Interactions of COVID-19 Vaccines Between Different Variants Among Age Groups", "Dec. 2021",
  "Lincoln Police Department | Statistics Internship", "Research Article", "Media and Police Officers: Media Depictions of Officers and Office Assumptions of Media Depictions", "Unpublished"
)%>%
  detailed_entries(
    Position,
    ProjectType,
    Desc,
    Year
  )
```

